Paper 2: Vitamin D

### 2017-11-08 doc/vitaminD.Rmd
vitamin D results for committee meeting document

# Box plot of uVDBP in different albuminuria categories
vitd %>% 
  box_plot("vitdStatus", "log(UDBP)", 
            "Vitamin D Status",
            "log uVDBP (μg/mmol)")

@@

dsBase %>% 
  scatter_plot_slides("log(udbpCr)", "VitaminD", 
               "log UDBP:Creatinine",
               "Serum 25(OH)D")

@@

plot_gee_results_vitd(gee_vitd_baseline,
                 yvars = "Serum 25(OH)D (nmol/L)")

@@

plot_gee_results_vitd(gee_vitd,
                 yvars = c("Serum 25(OH)D (nmol/L)",
                           "PTH (pmol/L)"))

>>>>

# Box plot of uVDBP in different albuminuria categories
vitd %>% 
  box_plot("vitdStatus", "log(udbpCr)", 
            "Vitamin D Status",
            "log uVDBP:cr (μg/mmol)")

@@

dsBase %>% 
  scatter_plot("log(udbpCr)", "VitaminD", 
               "log UDBP:Creatinine",
               "Serum 25(OH)D")

@@

plot_gee_results_vitd_base(gee_vitd_baseline,
                 yvars = "Serum 25(OH)D (nmol/L)")

@@

plot_gee_results_vitd(gee_vitd,
                 yvars = "Serum 25(OH)D (nmol/L)")
